Univalent Universes and Completness of Reversible Programs: \\ Featherweight HoTT

### 2017-03-02 upi.tex
a few more definitions

\paragraph*{Univalent Type Family.} A type family $P : A \to \mathcal{U}$ is
\emph{univalent} if the following function is an equivalence:
\[\begin{array}{rcl}
f & : & (x \equiv y) \to (P(x) \simeq P(y)) \\
\end{array}\]
where $x,y:A$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Univalence}

>>>>

\paragraph*{Univalent Type Family.} A type family $P : A \to \mathcal{U}$ is
\emph{univalent} if the following function is an equivalence:
\[\begin{array}{rcl}
V_P & : & (x \equiv y) \to (P(x) \simeq P(y)) \\
V_P &=& \lambda p. \mathit{idtoequiv}(\mathit{ap}_{P}(p))
\end{array}\]
where $x,y:A$ and the standard constructions from the book
$\mathit{ap} : (x \equiv y) \to (P(x) \equiv P(y)$ and
$\mathit{idtoequiv} : (A \equiv B) \to (A \simeq B)$.

\paragraph*{Example I.} Consider the type family
$\mathit{Id} : \mathcal{U} \to \mathcal{U}$. In this case, the function
$V_{\mathit{Id}}$ is $\mathit{idtoequiv}$ and the definition of univalent type
family reduces to the conventional univalence axiom.

\newpage
